TBD

### 2021-02-26 outputs/paper/paper.Rmd
Figure captioned and combined accordingly, results rearranged

```{r Q5Q6tTest, echo = FALSE, message = FALSE, tab.post = "H"}
### T-Tests (Welch's)
#Q5
control_q5 <-
  all_simulated_dataset %>%
  filter(type == "Control") %>%
  select(Q5)
treatment_q5 <-
  all_simulated_dataset %>%
  filter(type == "Treated") %>%
  select(Q5)
t3 <- t.test(control_q5, treatment_q5, paired = FALSE)
#Q6
control_q6 <-
  all_simulated_dataset %>%
  filter(type == "Control") %>%
  select(Q6)
treatment_q6 <-
  all_simulated_dataset %>%
  filter(type == "Treated") %>%
  select(Q6)
t4 <- t.test(control_q6, treatment_q6, paired = FALSE)

### Q5 + Q6 compiled t-test table
t_tests <- map_df(list(t3, t4), tidy) %>%
  subset(select = -c(alternative, method, conf.low, conf.high))

@@

In terms of effects on revenue and/or overall sales for restaurants during the intervention period, Figure 5 shows us that more restaurants within the treatment group saw decreases in revenue compared to the prior quarter (July 1 - Sep 30), while the control group's revenue largely remained the same. In addition to this, Figure 6 shows that of those restaurants that saw a decrease in revenue, the treatment group saw the harshest declines in revenue during the intervention period. A Chi-Square test for whether the restaurant saw a decrease in revenue showed that restaurants in the treatment group were more likely to report a decrease in revenue *X*^2^ (2, *N* = 330) = 220.73, *p* < 2.2e-16. The percentage decrease in revenues also showed a significant relationship, where restaurants in the treatment group are most likely to report higher loss of revenue during the intervention period *X*^2^ (3, *N* = 330) = 178.33, *p* < 2.2e-16. Prior to the intervention period, it appears as though both groups had similar breakdowns of revenue coming from take-out and/or delivery (Figure 7).

Questions related to the adjustments of the restaurants during the intervention, such as a menu price, and hours and days of operation (Figures 8-12) show us that:

@@

## Figures

### Sample Characteristics

```{r Q10, echo = FALSE, message = FALSE, fig.cap = "The most used food courier service"}
### Between Oct 1 and Dec 31, which food courier service did you receive the most orders from?
### UberEats
### SkiptheDishes 
### DoorDash
### Other
### In-house delivery service
### None
ggplot(data = all_simulated_dataset, mapping = aes(x = Q11, fill = type)) +
  geom_bar(position = "stack") + coord_flip() +
  scale_x_discrete(limit = c("UberEats", "SkiptheDishes", "DoorDash", "In-house delivery service", "Other", "None")) +
  labs(x = "Delivery Service",
       y = "# of Restaurants",
       title = "Food courier service popularity",
       fill = "Condition") +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) + 
  theme_fivethirtyeight()
```

### Effects of Intervention on Number of Employees

```{r Q5Q6mean, echo = FALSE, message = FALSE}
### Prior to (intervention start date), how many people did you employ?
### How many people do you currently employ?
t1 <-
all_simulated_dataset %>%
  group_by(type) %>%
  summarise(prior_employees = mean(Q5, na.rm = TRUE, .groups = NULL))
t2 <-
all_simulated_dataset %>%
  group_by(type) %>%
  summarise(curr_employees = mean(Q6, na.rm = TRUE), .groups = NULL)
total <- merge(t1, t2, by = c("type"))
# kable(total,
#       booktabs = T,
#       digits = 3,
#       col.names = c("Group Type",
#                   "# of Employees Prior to Intervention",
#                   "Current # of Employees")) %>%
#       footnote(general = "Change in # of employees before and after intervention period (Q5 + Q6)") %>%
#   kable_paper()
  # This table could be excluded because the means will be displayed anyway in the following T-test table?
```

```{r Q7, echo = FALSE, message = FALSE}
### Between Oct 1 and Dec 31 was your total sales revenue higher, lower, or about the same as it was during the previous quarter (last quarter dates)? *
### Higher
### Lower
### Around the Same
ggplot(data = all_simulated_dataset, mapping = aes(x = Q7, fill = type)) + 
  geom_bar() +
  labs(x = "Revenue Change",
       y = "# of Restaurants",
       title = "Revenue changes between Oct 1 and Dec 31",
       fill = "Condition") +
  theme_fivethirtyeight() + 
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))

### Chi-squared test
q7_chi <- table(all_simulated_dataset$Q7, all_simulated_dataset$type) %>%
  chisq.test()
tableChisq("Pearson's Chi-squared test to examine the possibility of an association between the intervention and the total sales", q7_chi$statistic, q7_chi$parameter, q7_chi$p.value)
```

```{r Q8, echo = FALSE, message = FALSE}
### What was the approximate percentage decrease in total sales revenue between Oct 1 and Dec 31 compared to the during the previous quarter (last quarter dates)? *
### Decline of 50% or more
### Decline of 25% to 50%
### Decline of 10% to 25%
### Decline of 10% or less
ggplot(data = all_simulated_dataset, mapping = aes (x = Q8, fill = type)) +
  geom_bar(position = "stack") + coord_flip() +
  scale_x_discrete(limit = c("Decline of 50% or more", "Decline of 25% to 50%", "Decline of 10% to 25%", "Decline of 10% or less")) + 
  labs(x = "Aprrox. % Decrease in Total Sales Revenue",
       y = "# of Restaurants",
       title = str_wrap("Percentage of total sales revenue decrease between Oct 1 and Dec 31", 40),
       fill = "Condition") +
  theme_fivethirtyeight() + 
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))

### Chi-squared test
q8_chi <- table(all_simulated_dataset$Q8, all_simulated_dataset$type) %>%
  chisq.test()
tableChisq("Pearson's Chi-squared test to examine the relation between the intervention and the total sales and a decline in revenue", q8_chi$statistic, q8_chi$parameter, q8_chi$p.value)
```

my_title = "Total revenue from takeout/delivery prior to Oct 1"
ggplot(data = all_simulated_dataset, mapping = aes (x = Q9, fill = type)) +
  geom_bar(position = "stack") +  coord_flip() + 
  scale_x_discrete(limit = c("Did not offer takeout or delivery", "25% or less", "25-50%", "50-75%", "75% or more")) + 
  labs(x = "Total Monthly Sales Revenue Fromt Takeout or Delivery",
       y = "# of Restaurants",
       title = str_wrap("Total revenue from takeout or delivery prior to Oct 1", 30),
       fill = "Condition") +
  theme_fivethirtyeight() + 
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))
```

## Effects of Intervention on Menu Prices

```{r Q11, echo = FALSE, message = FALSE}
### Between (start date of intervention) and (end date of intervention), did you make any adjustments to your menu prices?
### Yes, prices were raised
### Yes, prices were lowered
### No changes were made
ggplot(data = all_simulated_dataset, mapping = aes (x = Q10, fill = type)) +
  geom_bar() +  
  coord_flip() + 
  scale_x_discrete(limit = c("Yes, prices were raised", "Yes, prices were lowered", "No changes were made")) + 
  labs(x = "Adjustments to Menu Prices",
       y = "# of Restaurants",
       title = str_wrap("Menu adjustments between Oct 1 and Dec 31", 30),
       fill = "Condition") +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  theme_fivethirtyeight()

### Chi-squared test
q11_chi <- table(all_simulated_dataset$Q11, all_simulated_dataset$type) %>%
  chisq.test()
tableChisq("Pearson's Chi-squared test to examine the association of the intervention with price adjustments", q11_chi$statistic, q11_chi$parameter, q11_chi$p.value)
```

## Effects of Intervention on Hours/Days of Operation

```{r Q12, echo = FALSE, message = FALSE}
### Between (start date of intervention) and (end date of intervention) did you reduce your ### restaurant’s hours of operation?
### Yes
### No
ggplot(data = all_simulated_dataset, mapping = aes(x = Q12, fill = type)) +
  geom_bar(position = position_dodge(1)) +
  labs(x = "Reduction in hours of operation",
       y = "# of restaurants",
       title = str_wrap("Reducton in operating hours between Oct 1 and Dec 31", 30),
       fill = "Condition") +
  theme_fivethirtyeight() +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))

### Chi-squared test
q12_chi <- table(all_simulated_dataset$Q12, all_simulated_dataset$type) %>%
  chisq.test()
tableChisq("Pearson's Chi-squared Test for Q12", q12_chi$statistic, q12_chi$parameter, q12_chi$p.value)
```

```{r Q13, echo = FALSE, message = FALSE}
### If yes, approximately how many hours per week did you reduce by
### 15% or less
### 15-30%
### 30-50%
### 50-75%
### 75% or more
ggplot(data = all_simulated_dataset, mapping = aes(x = Q13, fill = type)) +
  geom_bar(position = "stack") +
  labs(x = "Hours Reduced per Week",
       y = "# of Restaurants",
       title = str_wrap("Percentage of hours reduced between Oct 1 and Dec 31", 30),
       fill = "Condition") +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  theme_fivethirtyeight()
```

```{r Q14, echo = FALSE, message = FALSE}
### Between (start date of intervention) and (end date of intervention) did you reduce the 
### number of days your restaurant was open to the public?
### Yes
### No 
ggplot(data = all_simulated_dataset, mapping = aes(x = Q14, fill = type)) +
  geom_bar(position = position_dodge(1)) +
  labs(x = "Reduction in Days of Operation",
       y = "# of Restaurants",
       title = str_wrap("Reduction of operating days between Oct 1 and Dec 31", 30),
       fill = "Condition") +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  theme_fivethirtyeight()

### Chi-squared test
q14_chi <- table(all_simulated_dataset$Q14, all_simulated_dataset$type) %>%
  chisq.test()
tableChisq("Pearson's Chi-squared Test for Q14", q14_chi$statistic, q14_chi$parameter, q14_chi$p.value)
```

```{r Q15, echo = FALSE, message = FALSE}
### If yes, how many days per week did you reduce by?
### 1-2 days
### 3-4 days
### 5-6 days
### 7 days
### Not Applicable
### bar graph/pie chart/line
ggplot(data = all_simulated_dataset, mapping = aes(x = Q15, fill = type)) +
  geom_bar(position = "stack") +
  labs(x = "Days Reduced",
       y = "# of Restaurants",
       title = "Reduction in days of operation per week",
       fill = "Condition") +
    scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  theme_fivethirtyeight()
```

>>>>

```{r Q5Q6tTest, echo = FALSE, message = FALSE, tab.post = "H"}
### T-Tests (Welch's)
#Q5
control_q5 <-
  all_simulated_dataset %>%
  filter(type == "Control") %>%
  select(Q5)
treatment_q5 <-
  all_simulated_dataset %>%
  filter(type == "Treated") %>%
  select(Q5)
t1 <- t.test(control_q5, treatment_q5, paired = FALSE)
#Q6
control_q6 <-
  all_simulated_dataset %>%
  filter(type == "Control") %>%
  select(Q6)
treatment_q6 <-
  all_simulated_dataset %>%
  filter(type == "Treated") %>%
  select(Q6)
t2 <- t.test(control_q6, treatment_q6, paired = FALSE)

### Q5 + Q6 compiled t-test table
t_tests <- map_df(list(t1, t2), tidy) %>%
  subset(select = -c(alternative, method, conf.low, conf.high))

@@

In terms of effects on revenue and/or overall sales for restaurants during the intervention period, Figure \@ref(fig:reveffects) shows us that more restaurants within the treatment group saw decreases in revenue compared to the prior quarter (July 1 - Sep 30), while the control group's revenue largely remained the same. In addition to this, it shows that of those restaurants that saw a decrease in revenue, the treatment group saw the harshest declines in revenue during the intervention period. A Chi-Square test for whether the restaurant saw a decrease in revenue showed that restaurants in the treatment group were more likely to report a decrease in revenue *X*^2^ (2, *N* = 330) = 220.73, *p* < 2.2e-16. The percentage decrease in revenues also showed a significant relationship, where restaurants in the treatment group are most likely to report higher loss of revenue during the intervention period *X*^2^ (3, *N* = 330) = 178.33, *p* < 2.2e-16. Prior to the intervention period, it appears as though both groups had similar breakdowns of revenue coming from take-out and/or delivery (Figure 7).

```{r Q7, echo = FALSE, message = FALSE}
### Between Oct 1 and Dec 31 was your total sales revenue higher, lower, or about the same as it was during the previous quarter (last quarter dates)? *
### Higher
### Lower
### Around the Same
q7 <- ggplot(data = all_simulated_dataset, mapping = aes(x = Q7, fill = type)) + 
  geom_bar() +
  labs(x = "Revenue Change",
       y = "# of Restaurants",
       title = "Revenue changes between Oct 1 and Dec 31",
       fill = "Condition") +
  theme_fivethirtyeight() + 
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))

### Chi-squared test
q7_chi <- table(all_simulated_dataset$Q7, all_simulated_dataset$type) %>%
  chisq.test()
#tableChisq("Pearson's Chi-squared test to examine the possibility of an association between the intervention and the total sales", q7_chi$statistic, q7_chi$parameter, q7_chi$p.value)
```

```{r Q8, echo = FALSE, message = FALSE}
### What was the approximate percentage decrease in total sales revenue between Oct 1 and Dec 31 compared to the during the previous quarter (last quarter dates)? *
### Decline of 50% or more
### Decline of 25% to 50%
### Decline of 10% to 25%
### Decline of 10% or less
q8 <- ggplot(data = all_simulated_dataset, mapping = aes (x = Q8, fill = type)) +
  geom_bar(position = "stack") + coord_flip() +
  scale_x_discrete(limit = c("Decline of 50% or more", "Decline of 25% to 50%", "Decline of 10% to 25%", "Decline of 10% or less")) + 
  labs(x = "Aprrox. % Decrease in Total Sales Revenue",
       y = "# of Restaurants",
       title = str_wrap("Percentage of total sales revenue decrease between Oct 1 and Dec 31", 40),
       fill = "Condition") +
  theme_fivethirtyeight() + 
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))

### Chi-squared test
q8_chi <- table(all_simulated_dataset$Q8, all_simulated_dataset$type) %>%
  chisq.test()
#tableChisq("Pearson's Chi-squared test to examine the relation between the intervention and the total sales and a decline in revenue", q8_chi$statistic, q8_chi$parameter, q8_chi$p.value)
```

q9 <- ggplot(data = all_simulated_dataset, mapping = aes (x = Q9, fill = type)) +
  geom_bar(position = "stack") +  coord_flip() + 
  scale_x_discrete(limit = c("Did not offer takeout or delivery", "25% or less", "25-50%", "50-75%", "75% or more")) + 
  labs(x = "Total Monthly Sales Revenue Fromt Takeout or Delivery",
       y = "# of Restaurants",
       title = str_wrap("Total revenue from takeout or delivery prior to Oct 1", 30),
       fill = "Condition") +
  theme_fivethirtyeight() + 
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))
```

```{r Q10, echo = FALSE, message = FALSE, fig.cap = "The most used food courier service"}
### Between Oct 1 and Dec 31, which food courier service did you receive the most orders from?
### UberEats
### SkiptheDishes 
### DoorDash
### Other
### In-house delivery service
### None
q10 <- ggplot(data = all_simulated_dataset, mapping = aes(x = Q11, fill = type)) +
  geom_bar(position = "stack") + coord_flip() +
  scale_x_discrete(limit = c("UberEats", "SkiptheDishes", "DoorDash", "In-house delivery service", "Other", "None")) +
  labs(x = "Delivery Service",
       y = "# of Restaurants",
       title = "Food courier service popularity",
       fill = "Condition") +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) + 
  theme_fivethirtyeight()
```

```{r reveffects, fig.width=12, fig.height=8, echo = FALSE, message = FALSE, fig.cap="Effects on revenue as a result of intervention by condition"}
grid.arrange(q7, q8, q9, q10)
```

Questions related to the adjustments of the restaurants during the intervention, such as a menu price, and hours and days of operation (Figure \@ref(fig:opseffects)) show us that:

@@

```{r Q11, echo = FALSE, message = FALSE}
### Between (start date of intervention) and (end date of intervention), did you make any adjustments to your menu prices?
### Yes, prices were raised
### Yes, prices were lowered
### No changes were made
q11 <- ggplot(data = all_simulated_dataset, mapping = aes (x = Q10, fill = type)) +
  geom_bar() +  
  coord_flip() + 
  scale_x_discrete(limit = c("Yes, prices were raised", "Yes, prices were lowered", "No changes were made")) + 
  labs(x = "Adjustments to Menu Prices",
       y = "# of Restaurants",
       title = str_wrap("Menu adjustments between Oct 1 and Dec 31", 30),
       fill = "Condition") +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  theme_fivethirtyeight()

### Chi-squared test
q11_chi <- table(all_simulated_dataset$Q11, all_simulated_dataset$type) %>%
  chisq.test()
#tableChisq("Pearson's Chi-squared test to examine the association of the intervention with price adjustments", q11_chi$statistic, q11_chi$parameter, q11_chi$p.value)
```

```{r Q12, echo = FALSE, message = FALSE}
### Between (start date of intervention) and (end date of intervention) did you reduce your ### restaurant’s hours of operation?
### Yes
### No
q12 <- ggplot(data = all_simulated_dataset, mapping = aes(x = Q12, fill = type)) +
  geom_bar(position = position_dodge(1)) +
  labs(x = "Reduction in hours of operation",
       y = "# of restaurants",
       title = str_wrap("Reducton in operating hours between Oct 1 and Dec 31", 30),
       fill = "Condition") +
  theme_fivethirtyeight() +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))

### Chi-squared test
q12_chi <- table(all_simulated_dataset$Q12, all_simulated_dataset$type) %>%
  chisq.test()
#tableChisq("Pearson's Chi-squared Test for Q12", q12_chi$statistic, q12_chi$parameter, q12_chi$p.value)
```

```{r Q13, echo = FALSE, message = FALSE}
### If yes, approximately how many hours per week did you reduce by
### 15% or less
### 15-30%
### 30-50%
### 50-75%
### 75% or more
q13 <- ggplot(data = all_simulated_dataset, mapping = aes(x = Q13, fill = type)) +
  geom_bar(position = "stack") +
  labs(x = "Hours Reduced per Week",
       y = "# of Restaurants",
       title = str_wrap("Percentage of hours reduced between Oct 1 and Dec 31", 30),
       fill = "Condition") +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  theme_fivethirtyeight()
```

```{r Q14, echo = FALSE, message = FALSE}
### Between (start date of intervention) and (end date of intervention) did you reduce the 
### number of days your restaurant was open to the public?
### Yes
### No 
q14 <- ggplot(data = all_simulated_dataset, mapping = aes(x = Q14, fill = type)) +
  geom_bar(position = position_dodge(1)) +
  labs(x = "Reduction in Days of Operation",
       y = "# of Restaurants",
       title = str_wrap("Reduction of operating days between Oct 1 and Dec 31", 30),
       fill = "Condition") +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  theme_fivethirtyeight()

### Chi-squared test
q14_chi <- table(all_simulated_dataset$Q14, all_simulated_dataset$type) %>%
  chisq.test()
#tableChisq("Pearson's Chi-squared Test for Q14", q14_chi$statistic, q14_chi$parameter, q14_chi$p.value)
```

```{r Q15, echo = FALSE, message = FALSE}
### If yes, how many days per week did you reduce by?
### 1-2 days
### 3-4 days
### 5-6 days
### 7 days
### Not Applicable
### bar graph/pie chart/line
q15 <- ggplot(data = all_simulated_dataset, mapping = aes(x = Q15, fill = type)) +
  geom_bar(position = "stack") +
  labs(x = "Days Reduced",
       y = "# of Restaurants",
       title = "Reduction in days of operation per week",
       fill = "Condition") +
    scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  theme_fivethirtyeight()
```

```{r opseffects, fig.width=11.5, fig.height=10, echo = FALSE, message = FALSE, fig.cap="Effects on hours and days of operation as a result of intervention by condition"}
grid.arrange(q11, q12, q13, q14, q15)
```
